---
title: "NoIR Plant Photosynthesis Measurement"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## take a NDVI picture of a plant to measure its photosynthesis

A Raspberry Pi with NoIR camera can be used to measure photosynthesis in plants. The infrared block filter (NoIR) has been removed from the camera. Adding a filter to block red light, allows the "red" channel of the camera to instead measure near-infrared light. Since chlorophyll absorbs blue and red light, but not green or infrared. The difference in red light absorption and near infrared reflectance indicates the amount of photosynthesis. Photos from the NOIR camera with red block filter can be processed into false-colored *Normalized Difference Vegetation Index* (NDVI) images using a free online tool, Infragram by Public Lab. 

https://www.raspberrypi.org/blog/whats-that-blue-thing-doing-here/  
https://publiclab.org/wiki/infragram  
https://publiclab.org/wiki/ndvi

## Normalized Difference Vegetation Index (NDVI) & photosynthesis

## NoIR camera & filter

## Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

## to do
1. create one-shot script for demo
2. get RPi & camera mounted with enclosure & filter
    camera mount hing pin, screw & nut, cover
3. try some plants, measuring other variables
4. write network setup procedure & try with another network (mom's?)
5. create handout
    motivation
    photosynthesis
    system description
    results
    
